Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-10 WSSSPE4_report/WSSSPE4_report.tex
adding link for flipchart photos

Once we had the walls covered in ideas, we had people organically form groups around the flip charts on the wall. \todo{find photos of flip charts, put in repo?} We asked them to work in Google Docs, \todo{find and cite these docs?  Is this really true, or was this all done in flip charts?} using a template for Vision, Gaps, and Projects.  For those folk who worked on Vision and Gaps, after an hour, we encouraged them to finish their Vision or Gap Google Doc, and to find and join or start working on a project with a group. This led to the 12 groups that are discussed in the rest of this section, specifically:
\begin{enumerate}
\item Verifying best practices \& metrics for sustainable research software
\item Software Sustainability Alliance
\item Scientific Software Prototyping Infrastructure (S2PI)
\item Standard metadata for software (CodeMeta)
\item White paper on developing sustainable softwarez
\item Social science for scientific software
\item Software best practices for undergraduates
\item Meaningful metrics for sustainable software
\item Coordinating access to CI for research software
\item Software engineering processes tailored for research software
\item Open research index
\item Letters of evaluation for computational scientists
\end{enumerate}

>>>>

Once we had the walls covered in ideas, we had people organically form groups around the flip charts on the wall\footnote{Photos of the flipcharts: \url{https://github.com/WSSSPE/media/tree/master/WSSSPE4-photos}}. We asked them to work in Google Docs, \todo{find and cite these docs?  Is this really true, or was this all done in flip charts?} using a template for Vision, Gaps, and Projects.  For those folk who worked on Vision and Gaps, after an hour, we encouraged them to finish their Vision or Gap Google Doc, and to find and join or start working on a project with a group. This led to the 12 groups that are discussed in the rest of this section, specifically:
\begin{enumerate}
\item Verifying best practices \& metrics for sustainable research software
\item Software Sustainability Alliance
\item Scientific Software Prototyping Infrastructure (S2PI)
\item Standard metadata for software (CodeMeta)
\item White paper on developing sustainable softwarez
\item Social science for scientific software
\item Software best practices for undergraduates
\item Meaningful metrics for sustainable software
\item Coordinating access to CI for research software
\item Software engineering processes tailored for research software
\item Open research index
\item Letters of evaluation for computational scientists
\end{enumerate}
